% resume.tex

% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{enumitem}
\usepackage{hyperref}

\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resdateitem}[2]{\item
\begin{tabular*}{6.95in}{l@{\extracolsep{\fill}}r}
		#1 & \textit{#2} \\
\end{tabular*}\vspace{-3pt}}
\newcommand{\noresrepeat}[0]{\vspace{-20pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Steven Roose}  & +32 484 73 97 53\\
\href{mailto:steven@stevenroose.org}{steven@stevenroose.org} & \\ 
\end{tabular*}
\\

\vspace{0.1in}


\resheading{Education}
\begin{itemize}[leftmargin=*]
\item[]
	\ressubheading{University of Leuven - Faculty of Engineering Science}{ }{
	Master of Engineering Science: Computer Science}{Sep. 2013 - Sep. 2017}
	\begin{itemize}
		\resitem{Specialization: Artificial Intelligence}
		\resitem{Thesis topic: Integrating cryptocurrencies with the Interledger
		protocol}
	\end{itemize}

	\ressubheading{\noresrepeat }{ }{Bachelor of Engineering Science}{Sep. 2010 - Jun. 2016}
	\begin{itemize}
		\resitem{Specialization: Computer Science, Electrical Engineering}
	\end{itemize}

\item[]
	\ressubheading{A.I. Class by Sebastian Thrun and Peter Norvig}{ }{Advanced Track of Introduction to Artificial Intelligence}{Sep. 2011 - Dec. 2011}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}[leftmargin=*]

\item[]
	\ressubheading{Blockstream}{ }{Core Tech Engineer}{Aug. 2018 - present}
	%\begin{itemize}
	%	\resitem{to fill...}
	%\end{itemize}

\item[]
	\ressubheading{Banco Santander Innovation Lab}{ }{Blockchain Engineer}{Oct. 2016 - Jun. 2018}
	\begin{itemize}
		\resitem{Evaluating different blockchain platforms and products for
		potential applications and developing proof-of-concepts.}
		\resitem{Designing and developing a cross-bank multi-currency payment
		and settlement system based on Ethereum.}
	\end{itemize}

\item[]
	\ressubheading{BeSt Designs}{ }{Web Developer}{2007 - 2012}
	%\begin{itemize}
	%	\resitem{Building websites featuring photo albums, contact forms, news updates, ... using basic web technology such as PHP, JavaScript, HTML and CSS.}
	%	\resitem{Integrating websites with existing CMS technologies and extending the WordPress functionality with a custom plugin.}
	%	\resitem{Utilizing the basic development process of extreme programming and feedback cycles with customers.}
	%\end{itemize}

\end{itemize}


\resheading{Open Source \hfill
\href{https://github.com/stevenroose}{github.com/stevenroose}}
\begin{itemize}[leftmargin=*]

\item[]
	\ressubheading{Pointy Castle}{\href{https://github.com/pointycastle}{github.com/pointycastle}}{Cryptography library for Dart developers}{ }
	\begin{itemize}
		\resitem{Cryptographic algorithms ported from Bouncy Castle or other sources.}
		\resitem{Reflection-based registry system that allows users to use custom implementations.}
	\end{itemize}

\item[]
	\ressubheading{Dartcoin}{\href{https://github.com/dartcoin}{github.com/dartcoin}}{Bitcoin implementation in the Dart language}{ }
	\begin{itemize}
		\resitem{Implementation of core Bitcoin protocol primitives with binary data serialization and parsing.}
		\resitem{Transaction signing and block validation.}
	\end{itemize}

\end{itemize}

\newpage

\resheading{Social Experience}
\begin{itemize}[leftmargin=*]

\item[]
	\ressubheading{Vlaamse Technishe Kring, VTK Leuven}{ }{Student Representative \& Volunteer}{Sep. 2015 - Aug. 2016}
	\begin{itemize}
		\resitem{Member of Board of Directors}
		\begin{itemize}
			\resitem{General decision-making about all activities and policies.}
			\resitem{Financial planning and evaluation of internal and external activities.}
		\end{itemize}
		\resitem{Vice-Coordinator Education}
		\begin{itemize}
			\resitem{Representing the students of the engineering faculty in different faculty meetings.}
			\resitem{Organizing student representation for all education within the faculty.}
		\end{itemize}
	\end{itemize}

\item[]
	\ressubheading{Scouts \& Gidsen Schilde, Scouting}{ }{Group Responsible}{Sep. 2012 - Aug. 2015}
	\begin{itemize}
			\resitem{Managing the day-to-day organization and motivating volunteers.}
			\resitem{Supervising the work and activities of leaders and resolving difficulties or conflicts.}
			\resitem{Communicating with the municipality, insurance providers, parents and the public.}
	\end{itemize}

	\ressubheading{\noresrepeat}{ }{Leader}{Sep. 2010 - Aug. 2015}
	\begin{itemize}
		\resitem{Preparing both entertainment and educational activities for children from 6 to 18 years old.}
		\resitem{Working together with other leaders to independently maintain our infrastructure and material.}
	\end{itemize}

\item[]
	\ressubheading{Youth Climate Conference Belgium}{Antwerp}{Co-organiser}{Sep. 12, 2009}
	\begin{itemize}
		\resitem{Educating youth about the issues of climate change and global warming.}
		\resitem{Polling for initiatives and opinions to represent Belgium at the European Youth Climate Conference.}
	\end{itemize}

\item[]
	\ressubheading{University of Leuven}{ }{Student Representative}{ }
	\begin{itemize}
		\resdateitem{Standing Education Commission Computer Science}{Sep. 2011 - Aug. 2016}
		\resdateitem{Council of the Faculty of Engineering Science}{Sep. 2012 - Aug. 2016}
		\resdateitem{Faculty Standing Education Commission}{Sep. 2015 - Aug. 2016} % name unsure
		\resdateitem{Student Services Council KU Leuven}{Sep. 2015 - Aug. 2016}
		\resdateitem{General Assembly of Student Council KU Leuven (Stura KU Leuven)}{Sep. 2015 - Aug. 2016}
		\resdateitem{General Assembly of Flemish Student Association (VVS)}{Sep. 2015 - Aug. 2016}
	\end{itemize}


\end{itemize}


\resheading{Skills}

\begin{description}
\item[Languages:]
Dutch, English (fluent), French, Portuguese, Spanish (understanding)
\item[Programming languages:]
Rust, Go, C++, Dart, Java, Python, Haskell, Prolog
\end{description}



\end{document}
